### 2022-10-19 manuscript/manuscript.tex
some pretty bgs stuff

Santiago and Caballero

@@

where $U$ is defined $U := 2 L \mu$, the deleterious mutation rate per diploid
genome, per generation. They then set $V_A = V_\text{BGS}$, and note that $V_m
\approx Us^2$, since mutations have frequency of $\nicefrac{1}{2N}$ and each
increase the variance by a factor of $s^2$. Note that because the classic BGS
model assumes deterministic selection dynamics (i.e. an infinite population),
the equilibrium $Z$ given by equation \eqref{eq:Z} excludes the reduction due
to drift, which reduces the variance by an additional factor $1 -
\nicefrac{1}{2N_e}$. Thus, the reduction factor under the strong BGS model is,

\begin{align}
  Z \left(1 - \frac{1}{2N_e}\right) = (1 - s)\left(1 - \frac{1}{2N_e}\right) \approx 1 - s -\frac{1}{2N_e}
\end{align}

(c.f. \cite{Santiago1998-bs} equation 10). An alternate derivation can be found
by working out the deterministic reduction in variance from the single-locus
dynamics. Thus, $Q' = $

the reduction under the classic BGS model is,

\begin{align}
  N_e = N \exp()
\end{align}

>>>>

Santiago and Caballero's approximation only keeps this first term, e.g. their
$Q_\infty^2 \approx 2/(L(1-Z))$, which is only accurate in the domain $L >
0.2$.

\begin{align}
  N_{e,\infty}^{\text(SC98)} \approx N \exp\left(-\frac{V_h}{(1-Z)L}\right) 
\end{align}

(c.f. \cite{Santiago1998-bs} equation 8). For small $L$, the small $\kappa$
approximation strongly deviates from the full equation; thus, throughout, we
use the unapproximated version,

\begin{align}
  N_{e,\infty}^* \approx N \exp\left(-\frac{V_h}{(1-Z) (2-(2-L) Z)} \right).
\end{align}

@@

where $U$ is defined $U := 2 L \mu$, the deleterious mutation rate per diploid
genome, per generation. They then set $V_A = V_\text{BGS}$, and note that $V_m
\approx Us^2$, since mutations have frequency of $\nicefrac{1}{2N}$ and each
increase the variance by a factor of $s^2$. Note that because the classic BGS
model assumes deterministic selection dynamics (i.e. an infinite population),
the equilibrium $Z$ given by equation \eqref{eq:Z} excludes the reduction due
to drift. The reduction factor under the strong BGS model is,

\begin{align}
  Z_\text{BGS} := 1 - \frac{Vm}{V_\text{BGS}} = 1 - \frac{Us^2}{Us} = 1 - s
\end{align}

(c.f. \cite{Santiago1998-bs} equation 10). An alternate derivation can be found
by working out the deterministic reduction in variance from the single-locus
dynamics.

Using $Z_\text{BGS}$, $V_m$, and $V$ under the background selection model, and
approximation $N_{e,\infty}^\text{SC98}$ (equation XXX), find an equation
reminiscent of the classic background selection with recombination results. We
find that by using the full equation XXX $N_{e,\infty}^*$ rather than the
approximation of Santiago and Caballero, the reduction due to background
selection is

\begin{align}
  N_{e,\infty}^\text{BGS} = N \exp\left( - \frac{U}{2s + L - Ls} \right)
\end{align}

which matches equation 8 of \textcite{Hudson1995-xc} up to the $Ls$ term and
equation 10 of \textcite{Nordborg1996-nq} up to the $2s$ term.
